---
title: "Aides Drug"
author: "Jennifer Dimmett"
date: "04/22/2020"
output: html_document
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
triUmp <-read.csv(file="triUmpsal.csv",header=TRUE)
```

```{r}
sexMaleData <- filter(triUmp, gender == "M")
sexFemaleData <- filter(triUmp, gender == "F")
drugUsersData <- filter(triUmp, DrugUser == "yes")
lbgtqData <- filter(triUmp, LGBTQ != "straight")
```


# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?.  If you skimp in this section expect to be marked down in your grade. Paint a picture of the project a couple of paragraphs is expected!-->

A new  preventative aides (triUmpsal) is under test in clinical trials. Analyze the effectiveness of this drug across the board. Consider population subgroups by gender, drug use, and sexual orientation. Finish this!

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method. Discuss what data manipulations may be needed for example subsetting or other binning procedures and what sort of graphical displays and inferential tools will be used!-->  

All variables in this study are categorical. As a result we use bar chart for graphical display, a cross table to summarize the numerical results, and a chi-square and/or fisher exact test for inference.

This will hold for all 5 questions.


### The first question is wether or not the vaccine was effective in the whole population. 

$H_O$ : The drug has no effect on wether or not one gets Aids.

$H_A$ : The drug does have an effect on whether or not one contracts Aids. 


### Results (Entire Population)

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->



### Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming or departing to what is expected by your null hypothesis !-->

```{r}
barchartGC(~infected + treatment , type = "percent", data=triUmp)
```

This barchart graph shows that the vaccine may have had an affect on whether participants aquire aids or not

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
table1 <- xtabs(~infected + treatment, data=triUmp)
rowPerc(table1)

colPerc(table1)
```


### Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->


```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```


# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

The P value < 0.05 therefore we reject the null hyphothesis.

We conclude that the evidence support that this drug does have an effect in the general population that wheter or not one acquires aids.


<!-- END !-->




### Question 2: Evaluation of drug efficacy for females only. 

$H_O$ : The drug has no effect on wether or not one gets Aids.

$H_A$ : The drug does have an effect on whether or not one contracts Aids. 


### Results (Female Population)

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->



### Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming or departing to what is expected by your null hypothesis !-->

```{r}
barchartGC(~infected + treatment , type = "percent", data=sexFemaleData)
```

This barchart graph shows that the vaccine may have had an affect on whether participants aquire aids or not

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
table2 <- xtabs(~infected + treatment, data=sexFemaleData)
rowPerc(table2)

colPerc(table2)
```


### Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->


```{r}
chisq.test(table2)
chisqtestGC(table2)
fisher.test(table2)
```


# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

The P value < 0.05 therefore we reject the null hyphothesis.

We conclude that the evidence support that this drug does have an effect in the female population which is detrimental and is increasing the chances of aquiring aids.



<!-- END !-->



### Question 3: Evaluation of drug efficacy for males only.

$H_O$ : The drug has no effect on wether or not one gets Aids.

$H_A$ : The drug does have an effect on whether or not one contracts Aids. 


### Results (Male Population)

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->



### Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming or departing to what is expected by your null hypothesis !-->

```{r}
barchartGC(~infected + treatment , type = "percent", data=sexMaleData)
```

This barchart graph shows that the vaccine may have had an affect on whether male participants aquire aids or not

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
table3 <- xtabs(~infected + treatment, data=sexMaleData)
rowPerc(table3)

colPerc(table3)
```


### Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->


```{r}
chisq.test(table3)
chisqtestGC(table3)
fisher.test(table3)
```


# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

The P value < 0.05 therefore we reject the null hyphothesis.

We have evidence to support the contention, that this drug does have an effect in the Male population that wheter or not one acquires aids.


<!-- END !-->




### Question 4: Evaluation of drug efficacy for Drug Users only.

$H_O$ : The drug has no effect on wether or not one gets Aids.

$H_A$ : The drug does have an effect on whether or not one contracts Aids. 


### Results (Drug User Population)

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->



### Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming or departing to what is expected by your null hypothesis !-->

```{r}
barchartGC(~infected + treatment , type = "percent", data=drugUsersData)
```

This barchart graph shows that the vaccine may have had an affect on whether Drug User participants aquire aids or not

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
table4 <- xtabs(~infected + treatment, data=sexMaleData)
rowPerc(table4)

colPerc(table4)
```


### Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->


```{r}
chisq.test(table4)
chisqtestGC(table4)
fisher.test(table4)
```


# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

The P value < 0.05 therefore we reject the null hyphothesis.

We have evidence to support the contention, that this drug does have an effect in the Drug User population that wheter or not one acquires aids.


<!-- END !-->



### Question 5: Evaluation of drug efficacy for only LBGTQ. 

$H_O$ : The drug has no effect on wether or not one gets Aids.

$H_A$ : The drug does have an effect on whether or not one contracts Aids. 


### Results (LBGTQ Population)

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->



### Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming or departing to what is expected by your null hypothesis !-->

```{r}
barchartGC(~infected + treatment , type = "percent", data=lbgtqData)
```

This barchart graph shows that the vaccine may have had an affect on whether participants aquire aids or not

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
table5 <- xtabs(~infected + treatment, data=sexFemaleData)
rowPerc(table5)

colPerc(table5)
```


### Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->


```{r}
chisq.test(table5)
chisqtestGC(table5)
fisher.test(table5)
```


# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

The P value < 0.05 therefore we reject the null hyphothesis.

We conclude that the evidence support that this drug does have an effect in the LBGTQ population which is detrimental and is increasing the chances of aquiring aids. 
